Quality Assessment of OpenStreetMap Footpath Data

### 2020-08-19 report/report.tex
Add spacing around the abstract section
Make it clear that the accuracy estimate methods are based on the Fan paper
Update information on DP

As a secondary study, the positional accuracy of the OSM dataset was calculated, since the positional accuracy determines the maximum tolerance in distance between points before it is certain that a road overlaps with another road or building.
Any geodataset has a limit on its positional accuracy, which is determined by the theoretical precision of the measuring methods.
In this project, the accuracy was obtained by comparing coordinate points of OSM building footprints to those in the Swedish University of Agricultural Sciences (SLU) building dataset, whose accuracy is known.

\end{abstract}

@@

Som en andra del av studien har felmarginalen för OSM-datamängden också tagits fram, eftersom felmarginalen bestämmer toleransen mellan två punkter som kan tillåtas innan man är säker på att en väg börjar överlappa med en annan väg eller en byggnad.
Varje geodatamängd har en gräns på hur väl den stämmer överrens med verkligheten, som bestäms av vilka mätmedoter som har använts i datans insamling.
I detta projekt uppskattades felmarginalen genom att jämföra byggnaders koordinatpunkter i datamängen med de från en referenskarta från Svenska Lantbruksuniversitetet (SLU) med känd felmarginal.

\end{abstract}
\end{otherlanguage}

@@

The geodata precision study has been carried out in a number of steps that are all detailed below.
First a feature map was found, which mapped individual features between the OSM dataset and a reference dataset.
A program then took matching building pairs and extracted matching geometrical points after first simplifying the polygons using the Douglas-Peucker algorithm by \textbf{(Douglas and Peucker, 1973)}.
Once a set of matching points has been found across the whole dataset, the average distance between them was taken as a measure of the positional accuracy.

@@

The final problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship, since footprints from different datasets may be formed at a different level of detail.
Possible problems are that the vertex counts could be dissimilar, or that vertex clusters may be found at different parts of the two polygons.
To avoid this effect, key points are extracted using the Douglas-Peucker algorithm \textbf{(Douglas and Peucker, 1973)}, to create a simplified footprint with less points that still retain information about the rough features of the detailed footprint.
The idea behind Douglas-Peucker is to recursively divide a polyline.
It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$.
It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$.
Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded.
See Algorithm 1 for a detailed view.
Following this, the Oriented Minimum Bounding Rectangles (OMBR) are calculated for both the simplified polygons.
Finally the OMBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the OMBR of the SLU building footprint.
Any edges in the simplified footprints that coincide with the OMBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.
See figure \ref{fig:vertex-match-algo} for an illustration of the algorithm that detects matching vertices between two similar polygons.

@@

Finally, when two building footprints and their vertices have been mapped, the average offset of matching vertices will be used as a measure of positional error.
The average and variance in vertex spread will be calculated and used to make an assessment of the geometric precision of the OSM dataset, and this precision will further be used to form an upper boundary on geometrical corrections that can be made in the overlap study.

>>>>

As a secondary study, the positional accuracy of the OSM dataset was calculated, since the positional accuracy determines the maximum tolerance in distance between points before it is certain that a road overlaps with another road or building.
Any geodataset has a limit on its positional accuracy, which is determined by the theoretical precision of the measuring methods.
In this project, the accuracy was obtained by comparing coordinate points of OSM building footprints to those in the Swedish University of Agricultural Sciences (SLU) building dataset, whose accuracy is known.
\end{abstract}

@@

Som en andra del av studien har felmarginalen för OSM-datamängden också tagits fram, eftersom felmarginalen bestämmer toleransen mellan två punkter som kan tillåtas innan man är säker på att en väg börjar överlappa med en annan väg eller en byggnad.
Varje geodatamängd har en gräns på hur väl den stämmer överrens med verkligheten, som bestäms av vilka mätmedoter som har använts i datans insamling.
I detta projekt uppskattades felmarginalen genom att jämföra byggnaders koordinatpunkter i datamängen med de från en referenskarta från Svenska Lantbruksuniversitetet (SLU) med känd felmarginal.
\end{abstract}
\end{otherlanguage}

@@

The methods used for the geodata precision study were largely based on those used by \textbf{(Fan et al, 2014)} in their study of the quality of the OSM Munich dataslice in 2014.
First a feature map was found, which mapped individual features between the OSM dataset and a reference dataset.
A program then took matching building pairs and extracted matching geometrical points after first simplifying the polygons using the Douglas-Peucker algorithm by \textbf{(Douglas and Peucker, 1973)}.
Once a set of matching points has been found across the whole dataset, the average distance between them was taken as a measure of the positional accuracy.

@@

Once a feature map has been obtained, the next task will be to find a matching vertex set among the vertices of the corresponding building footprint polygons.
Provided that the corresponding building footprints are true representations of the real life building, these pairs of matching verties must match the same part of the building.
The most common case is that a vertex represents a corner in the footprint polygon, and in these cases it must hold that two matching vertices represent the same corner.
The central problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship, since footprints from different datasets may be formed at a different level of detail.
Possible causes are that the vertex counts are dissimilar, or that vertex clusters may be found at different parts of the two polygons.
Thus, simply comparing the closest vertices between the two building representations may not be valid, since those vertices may not represent the same part of the true building footprint.
To avoid this effect, key points were extracted using the Douglas-Peucker algorithm \textbf{(Douglas and Peucker, 1973)}, to create a simplified footprint with less points that still retain information about the rough features of the detailed footprint.
This will eliminate dense vertex clusters, as well as any vertices that lie in roughly straight lines, in favour of creating polygons with reduced vertex counts.
A useful property of the Douglas-Peucker algorithm is that two highly similar polygons of different vertex counts will be reduced to resulting polygons with similar vertex counts.
Thus, one can be much more certain that a closest vertex pair is indeed corresponding to the same feature of the building.

The idea behind Douglas-Peucker is to recursively divide a polyline.
It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$.
It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$.
Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded.
See Algorithm 1 for a detailed view.
Following this, the Oriented Minimum Bounding Rectangles (OMBR) are calculated for both the simplified polygons.
Finally the OMBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the OMBR of the SLU building footprint.
Any edges in the simplified footprints that coincide with the OMBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.
See figure \ref{fig:vertex-match-algo} for an illustration of the algorithm that detects matching vertices between two similar polygons.

@@

Finally, when two building footprints and their vertices have been mapped, the average offset of the matching vertices will be used as a measure of positional error.
The final estimate of the positional accuracy of the OSM dataset will be taken as the average of each building's positional error, over the entire dataset.
The average and variance in vertex spread will be calculated and used to make an assessment of the geometric precision of the OSM dataset, and this precision will further be used to form an upper boundary on geometrical corrections that can be made in the overlap study.
